Painting with Triangles

### 2014-06-06 paper.tex
Final edit, per Adam's suggestion.

\section{Results and Discussion}
Paintings made with our system in a range of visual styles are shown in Figures~\ref{fig:teaser} and \ref{fig:face}--\ref{fig:stop}.  
%
The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our renderer begins to suffer from artifacts at 
the limits of single floating point precision; 
this could be ameliorated by switching to double-precision. 
\modified{Nevertheless, this range far exceeds limits
imposed by existing vector graphics software such as Adobe Illustrator, which has a maximum zoom ratio
of 64:1.  Furthermore, our ability to make paint strokes of smooth gradients in a flat vector representation (\eg, Figure~\ref{fig:teaser}) is unique.}

>>>>

\section{Results and Discussion}
Paintings made with our system in a range of visual styles are shown in Figures~\ref{fig:teaser} and \ref{fig:face}--\ref{fig:stop}.  
%
The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our renderer begins to suffer from artifacts at 
the limits of single floating point precision; 
this could be ameliorated by switching to double-precision. 
\modified{Nevertheless, this range far exceeds limits
imposed by existing vector graphics software such as Adobe Illustrator, which has a maximum zoom ratio
of 64:1.  Furthermore, the ability to make paint strokes of smooth gradients in a flat vector representation (\eg, Figure~\ref{fig:teaser}) differentiates our approach from previous methods.}
